Linear variation and an optimization of algorithms for connected components labeling in a binary image

### 2016-02-02 paper/paper.tex
Fix title and integral limits placement

\title{Optimization for connected-component counting in binary image for the case of
8-connectivity}

@@

\begin{abstract}
The linear variation is a topological characteristic of the function of two variables.
The problem of linear variation computing can be reduced to the problem
of counting connected components in a binary image with eight-connected connectivity.
The new hybrid method for the problem is presented.
The method is essentially a modification of a two-scan algorithm for labeling
that groups the pixels into $2 \times 2$ cells.

@@

\begin{equation}
  TV(u) = \int_{\Omega} |\nabla u|\,dx\,dy.
  \label{eq:TV}
\end{equation}

@@

Let $\Phi_u(t)$ be the number of regular components of a level set $t$
for a continuous function.
The first Kronrod's linear variation is defined as
\begin{equation}
  V(u) = \int_{-\infty}^{+\infty} \Phi_u(t)\,dt.
  \label{eq:KronrodVariation}
\end{equation}

@@

This paper presents an efficient way to convert the initial binary image
with 8-connectivity into
a condensed (non-binary) image with new connectivity that is $2$ times smaller in
each dimension than the initial image.
Most approaches for CC labeling are still valid for the new matrix.
As time and memory consumptions of conventional approaches usually depend linearly on
the number of pixels, running them on the condensed image can be up to 4 times
more efficient than running on the initial image.

>>>>

\title{Linear variation and an optimization of algorithms for connected
components labeling in a binary image}

@@

\begin{abstract}
Linear variation is a topological characteristic of a function of two variables.
The problem of linear variation computing can be reduced to the problem
of counting connected components in a binary image with eight-connected connectivity.
The new hybrid method for the problem is presented.
The method is essentially a modification of a two-scan algorithm for labeling
that groups the pixels into $2 \times 2$ cells.

@@

\begin{equation}
  TV(u) = \int\limits_{\Omega} |\nabla u|\,dx\,dy.
  \label{eq:TV}
\end{equation}

@@

Let $\Phi_u(t)$ be the number of regular components of a level set $t$
for a continuous function.
The first Kronrod's linear variation is defined as
\begin{equation}
  V(u) = \int\limits_{-\infty}^{+\infty} \Phi_u(t)\,dt.
  \label{eq:KronrodVariation}
\end{equation}

@@

This paper presents an efficient way to convert the initial binary image
with 8-connectivity into
a condensed (non-binary) image with new connectivity that is $2$ times smaller in
each dimension than the initial image.
Most approaches for CC labeling are still valid for the new image.
As time and memory consumptions of conventional approaches usually depend linearly on
the number of pixels, running them on the condensed image can be up to 4 times
more efficient than running on the initial image.
